### 2018-11-14 Sections/essay_security_implications_of_the_global_quantum_internet.tex
Minor edits
Resized figs for 1 column
trump

Combined with encrypted quantum computing protocols\index{Encrypted quantum computation}, no one would even know what they were up to when using this awesome computing power, and what they learn, they could keep to themselves.
\if 1\pubmode
\else
Alg.~\ref{alg:russian} describes a typical protocol for a particularly nefarious application for this, with the end result shown in Fig.~\ref{fig:trump_tweet}\footnote{\textit{``I don't even know why any of us are here. This is the worst job I've ever had."}}.

@@

\begin{figure}[!htbp]
\includegraphics[clip=true, width=0.475\textwidth]{trump_tweet}
\captionspacefig \caption{POTUS responds to Alg.~\ref{alg:russian}.}\label{fig:trump_tweet}\index{Trump}\index{Sad}\index{Covfefe}
\end{figure}
\fi

@@

\comment{Talk about QKD, post-classical crypto, halving private key lengths. hacking stored public-key encrypted data from past is a security threat even once we have transitioned to post-classical crypto. NSA probably has mass storage of collected, but as yet uncracked data. now they can work back through it.}

>>>>

Combined with encrypted quantum computing protocols\index{Encrypted quantum computation}, no one would even know what they were up to when using this awesome computing power, and what they learn, they could keep to themselves.

Alg.~\ref{alg:russian} describes a typical protocol for a particularly nefarious application for this, with the end result shown in Fig.~\ref{fig:trump_tweet}\footnote{\textit{``I don't even know why any of us are here. This is the worst job I've ever had."}}.

@@

\begin{figure}[!htbp]
\if 3\pubmode
\includegraphics[clip=true, width=0.6\textwidth]{trump_tweet}
\else
\includegraphics[clip=true, width=0.475\textwidth]{trump_tweet}
\fi
\captionspacefig \caption{POTUS responds to Alg.~\ref{alg:russian}.}\label{fig:trump_tweet}\index{Trump}\index{Sad}\index{Covfefe}
\end{figure}

@@

\comment{Talk about QKD, post-classical crypto, halving private-key lengths. hacking stored public-key encrypted data from past is a security threat even once we have transitioned to post-classical crypto. NSA probably has mass storage of collected, but as yet uncracked data. now they can work back through it.}
